---
title: "01: Basics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bregr)
```


#' # Generalized Linear (GLM) Model
#' m1 <- br_set_data(data) |>
#'   br_set_y("counts") |>
#'   br_set_x(x = "outcome", x2 = "treatment")) |>
#'   br_set_model("poisson") |>
#'   br_run()
#' m1
#'
#' # Cox-PH Model
#'
#' # 2. Model Batch Processing ---------------
#' # 3. Group Modeling -----------------------

#' library(survival)
#' library(bregr)
#'
#' data <- data.frame(
#'   counts = c(18, 17, 15, 20, 10, 20, 25, 13, 12),
#'   outcome = gl(3, 1, 9),
#'   treatment = gl(3, 3)
#' )
#' 
#' # 1. Single Model -------------------------
#'
#' # Generalized Linear (GLM) Model
#' m1 <- br_set_data(data) |>
#'   br_set_y("counts") |>
#'   br_set_x(x = "outcome", x2 = "treatment")) |>
#'   br_set_model("poisson") |>
#'   br_run()
#' m1
#'
#' # Cox-PH Model
#'
#' # 2. Model Batch Processing ---------------
#' # 3. Group Modeling -----------------------
#'
#'
#' br_set_data(data) |>
#'   br_set_y(c("time", "status")) |>
#'   br_set_x(c("age", "sex"), "ph.ecog") |>
#'   br_set_model("coxph") |>
#'   br_run()
#'
#' br_set_data(data) |>
#'   br_set_y(c("time", "status")) |>
#'   br_set_x(c("age", "sex"), "ph.ecog") |>
#'   br_set_model("coxph") |>
#'   br_run()
#'
#' br_set_data(data) |>
#'   br_set_y(c("time", "status")) |>
#'   br_set_x(c("age * sex"), "pat.karno") |>
#'   br_set_model("coxph") |>
#'   br_run(exponentiate = TRUE, conf.level = 0.90)
#'
#' br_set_data(data) |>
#'   br_set_y(c("time")) |>
#'   br_set_x(c("age", "sex"), "pat.karno") |>
#'   br_set_model('quasi(variance = "mu", link = "log")') |>
#'   br_run()
#'
